{\boldmath Pseudoscalar top-Higgs coupling: Exploration of $\mathrm{CP}$-odd observables to resolve the sign ambiguity }

### 2016-03-04 Paper_ttbarH_Draft.tex
KK edits up through Sec. VI

For comparison purposes, we have also used our simulated events
to test the asymmetry corresponding to the lab frame observable given
in Ref.~\cite{Guadagnoli}. {\bf (KK: Is this lab frame observable
  just a TP, like we have used?  It seems strange to talk about an
  asymmetry associated with an observable, when normally an asymmetry
  is itself considered to be an observable.  I'm wondering if we are
  considering an asymmetry associated with a TP, or if we are actually
  just looking at whatever observable they have defined\ldots.  Sorry for
  my confusion on this!)}  We have found that this observable
{\bf (KK: ``asymmetry''?)}
appears to
be slightly less sensitive than the combination $\epsilon_{10}$,
{\bf (KK: ``$\mathcal{A}(\epsilon_{10})$''?)}
giving rise to a separation between the $\mathrm{CP}$-mixed scenarios
that is smaller by about $1.4\sigma$.
\section{Experimental Feasibility}
\label{sec6}
By considering the mild selection cuts introduced in Sec.~\ref{sec3},
the SM cross section for $\ppprocess$, $\ell=e,\mu$ at
$14\,\mathrm{TeV}$ is $\sim 15.3\,\mathrm{fb}$ and hence the number of
events expected within the context of the HL-LHC is $\sim
15.3\,\mathrm{fb} \times 3000\,\mathrm{fb}^{-1} = 4.59\times
10^4$. This number is expected to be even larger in the case of
$\kp=1,\kpt\neq 0$ since the corresponding cross section is then
higher than the SM one. By taking into account NLO corrections to the
production process and considering a $K$-factor around $1.2$
\cite{Dawson,Beenakker,Dittmaier}, the number of events can be raised
up to $\sim 5.49 \times 10^4$. On the other hand, additional cuts as
well as the efficiency related to the reconstruction of particles
momenta will contribute to decrease this number. For instance, in
order to obtain the asymmetry of $\epsilon_4$, the $t$ and $\tbar$
momenta need to be reconstructed. This is challenging not only due to
the presence of two neutrinos in the final state which escape the
detector undetected but also because final state objects need to be
asocciated with the respective parent quark \cite{atlasconf}. As was
already mentioned in Sec.~\ref{sec5}, a possibility is to use the
neutrino weighting technique along with the kinematic equations
arising from kinematic constraints related to the top and $W$ masses
as well as from the energy-momentum conservation at each of the decay
vertices involved in the process. Within the context of $t\tbar$ this
procedure has been used, for instance, in order to obtain measurements
of spin correlation \cite{atlasconf} and charge asymmetry
\cite{atlascharge}. Also, events reconstructed with this technique has
been used in \cite{dosSantos} for analyzing angular distributions that
are useful for discriminating the signal from the backgrounds in
$t\tbar H (H\rightarrow b\bbar)$. In all these cases the corresponding
efficiency in the reconstruction of the momenta is up to $\sim 80
\%$.\par Based on the discussion given in the previous paragraph, we
have simulated sets of $5\times 10^4, 1\times 10^4$ and $5\times 10^3$
events and recalculated the most sensitive observable, namely
$\mathcal{A}(\epsilon_4)$, for each case. The results are displayed in
Table \ref{table11}, where it can be seen that for a number of events
close to that roughly estimated above within the context of the
HL-LHC, the observable is still sensitive to $\kpt$ allowing to
separate the $\mathrm{CP}$-mixed cases by $19\sigma$. As expected, the
sensitivity worsen as the number of events is reduced, but even with
$5\times 10^3$ events the separation between the $\mathrm{CP}$-mixed
hypotheses under consideration is around $6.5\sigma$. \par Although
the combination $\epsilon_{10}$ discussed in Sec.~\ref{sec5} avoids
the problem of reconstructing the top and antitop momenta, we have
also considered the respective asymmetry obtained for more
conservative numbers of events. In Table \ref{table12} we show the
results for $\mathcal{A}(\epsilon_{10})$ when the number of events is
reduced from $5\times 10^4$ to $1\times 10^4$. We see in this case
that even with $1\times 10^4$ simulated events the observable is
capable to discriminate the $\mathrm{CP}$-mixed cases by
$5.6\sigma$.\par Finally, it is important to mention that a realistic
analysis of the sensistivity of the observables discussed in this
paper requires the study of the impact of the backgrounds as well as
the hadronization of the quarks in the final state and the effects of
the detector. If we consider the dominant decay mode of the higgs,
$H\rightarrow b\bbar$, in order to maximize the cross section of the
process, the signature is given by $4$ $b$-jets, two leptons and
missing energy, while the main background arise from the production of
$t\tbar$ in asocciation with additional jets, being the dominant
source the production of $t\tbar + b\bbar$. By applying a small set of
cuts it is shown in \cite{chinos} that the
\begin{table}[H]
\caption{Asymmetry for the TP $\epsilon_4$ obtained by using $5\times
  10^4, 1 \times 10^4$ and $5\times 10^3$ simulated events for the SM
  case and the two $\mathrm{CP}$-mixed cases defined by
  $\kp=1,\kpt=\pm 1$. }
\label{table11}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|========|}
%\hhline{|--------|}
\multirow{2}{*}{$\kappa_t$} & \multirow{2}{*}{$\tilde{\kappa}_t$} & \multicolumn{2}{c||}{$N_{\mathrm{ev}}=5\times 10^4$} & \multicolumn{2}{c||}{$N_{\mathrm{ev}}=1\times 10^4$} & \multicolumn{2}{c|}{$N_{\mathrm{ev}}=5\times 10^3$} \\ \cline{3-8}
& & $\mathcal{A}(\epsilon_4)$~~&$\mathcal{A}(\epsilon_4)/\sigma_{\mathcal{A}}$ &  $\mathcal{A}(\epsilon_4)$~~&$\mathcal{A}(\epsilon_4)/\sigma_{\mathcal{A}}$ &  $\mathcal{A}(\epsilon_4)$~~&$\mathcal{A}(\epsilon_4)/\sigma_{\mathcal{A}}$ \\
\hhline{|========|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $-0.0405$~~~ & $-9.1$~~~ & $-0.0426$~~~ & $-4.3$~~~ & $-0.0496$~~~ & $-3.5$~~~ \\[0.6mm]
\hline
$1$ & $0$ & $0.0004$~ & $0.1$~ & $-0.0084$~~~ & $-0.8$~~~ & $-0.0004$~~~ & $-0.03$~~~ \\[0.6mm]
\hline
$1$ & $1$ & $0.0443$~ & $9.9$~ & $0.0434$~ & $4.2$~ & $\,0.0420$~ & $3.0\,\,$ \\
\hhline{|========|}
%\hhline{|--------|}
\end{tabular}
\end{table}
\begin{table}[H]
\caption{Asymmetry for the TP $\epsilon_{10}$ in the SM case and the
  two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$ when the
  number of simulated events is reduced from $5\times 10^4$ to $1
  \times 10^4$.}
\label{table12}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|======|}
%\hhline{|--------|}
\multirow{2}{*}{$\kappa_t$} & \multirow{2}{*}{$\tilde{\kappa}_t$} & \multicolumn{2}{c||}{$N_{\mathrm{ev}}=5\times 10^4$} & \multicolumn{2}{c|}{$N_{\mathrm{ev}}=1\times 10^4$} \\ \cline{3-6}
& & $\mathcal{A}(\epsilon_{10})$~~&$\mathcal{A}(\epsilon_{10})/\sigma_{\mathcal{A}}$ &  $\mathcal{A}(\epsilon_{10})$~~&$\mathcal{A}(\epsilon_{10})/\sigma_{\mathcal{A}}$ \\
\hhline{|======|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $-0.0270$~~~ & $-6.0$~~~ & $-0.0184$~~~ & $-1.8$~~~  \\[0.6mm]
\hline
$1$ & $0$ & $0.0022$~ & $0.5$~ & $-0.0086$~~~ & $-0.9$~~~  \\[0.6mm]
\hline
$1$ & $1$ & $0.0313$~ & $7.0$~ & $0.0380$~ & $3.8\,$ \\
\hhline{|======|}
%\hhline{|--------|}
\end{tabular}
\end{table}
\noindent
signal to background ratio is largely improved. On the other hand, a
rigorous treatment of the backgrounds and their impact with respect to
the signal is performed in \cite{atlasger} by using $20.3\,
\mathrm{fb}^{-1}$ of data at $\sqrt{s}=8\,\mathrm{TeV}$.  \par The
results shown in tables \ref{table11} and \ref{table12} reveal that
with $5\times 10^3$ and $1\times 10^4$ events respectively the
observables $\mathcal{A}(\epsilon_4)$ and $\mathcal{A}(\epsilon_{10})$
are still useful for testing $\kpt$. Without considering the lack of
events related to the experimental analysis, these numbers of events
correspond to a luminosity around $\sim
300\,$-$\,600\,\mathrm{fb}^{-1}$ for the SM and even smaller for the
$\mathrm{CP}$-mixed cases due to the larger cross section. This range
of luminosities is in principle achievable in the short term by the
LHC. We note that in order to be fully conclusive about the required
luminosity, it is important to include the effects of hadronization,
detector resolution, reconstruction eficciencies and so
forth. However, this kind of analysis is out of the scope of this
paper.
%%%%%%%%%%%% with Cuts
%51.46/17 -0.02 +- 0.08
%45.48/17  -1.09 +- 0.07
%65.60/17   0.96 +- 0.08
%28.84/17   0.02 +- 0.07
%%%%%%%
%9.13/17     0.01 +- 0.06
%9.05/17     -0.98 +- 0.07
%19.7/17     0.80 +- 0.07
%16.59/17    0.06 +- 0.07
%%%%%%%%%%%% without Cuts
%16.36/17    0.0022 +-0.06
%15.25/17    -0.82 +- 0.07
%12.80/17    0.81 +- 0.07
%19.38/17    0.11 +- 0.08
%%%%%%
%7.45/17    0.005 +- 0.06
%18.17/17   -0.77 +- 0.07
%9.59/17    0.73 +- 0.06
%12.39/17   0.09 +- 0.08
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec7}
In this paper we have presented a collection of $\mathrm{CP}$-odd
observables based on triple product correlations that are useful for
disentangling the relative sign between the scalar ($\kp$) and a
potential pseudoscalar ($\kpt$) top-Higgs couplings in the $t\tbar H$
production with both tops decaying leptonically. We have tested the
sensitivity of the proposed observables by considering three types of
observables: asymmetries, mean values and angular distributions.\par

Through the use of spinor techniques we have written the expression
for the differential cross section of the full process in such a
manner that the production and the decay parts are separated, although
connected by the spin vectors of the top and antitop which are given
in terms of the momenta of the leptons in the final state. Moreover,
we have indentified the terms linear in $\kp$ and $\kpt$ as those
involving TPs. Among these, we have explored the three that do not
involve the momenta of the incoming quarks/gluons and at the same time
incorporate both spin vectors: $\epsilon_1\equiv \TPa$,
$\epsilon_2\equiv \TPb$ and $\epsilon_3\equiv \TPc$.\par We have found
that $\epsilon_{1,2,3}$ allow to distinguish between the
$\mathrm{CP}$-mixed hypotheses by more than $\sim 20\sigma$ in the
case of asymmetries and $\sim 10\sigma$ in the case of mean values
when $1 \times 10^5$ simulated events are used. Furthermore, we have
shown that the angular distributions asocciated with these TPs are
also sensitive to the value of $\kp$ and $\kpt$ exhibiting a phase
shift that varies according to the values taken by these couplings. On
the other hand, by exploring TPs that incorporate the momenta of the
Higgs and the leptons instead of the spin vectors we can conclude that
the observables studied here appear to be more sensitive when the spin
vectors are used.\par

>>>>

For comparison purposes, we have also used our simulated events
to test the asymmetry corresponding to the lab frame observable given
in Ref.~\cite{Guadagnoli}. {\bf (KK: Is this lab frame observable
  just a TP, like we have used?  It seems strange to talk about an
  asymmetry associated with an observable, when normally an asymmetry
  is itself considered to be an observable.  I'm wondering if we are
  considering an asymmetry associated with a TP, or if we are actually
  just looking at whatever observable they have defined\ldots.  Sorry for
  my confusion on this!)}  We have found that this observable
{\bf (KK: ``asymmetry''?)}
appears to
be slightly less sensitive than the combination $\epsilon_{10}$,
{\bf (KK: ``$\mathcal{A}(\epsilon_{10})$''?)}
giving rise to a separation between the $\mathrm{CP}$-mixed scenarios
that is smaller by about $1.4\sigma$.

%
\section{Experimental Feasibility}
\label{sec6}
%

In our numerical analyses so far we have used relatively large
samples of events ($10^5$ events per sample)
in order to clearly distinguish
which observables would be most promising.  
The number of events expected at the HL-LHC, however, is
smaller than the number of events that we have used in our
simulations.  In this section we reexamine
the more promising observables, using sample sizes that are
more attainable in the near future.  {\bf (KK: OK?)}

Let us first make some estimates regarding the number of signal events
expected at the HL-LHC.
In Sec.~\ref{sec3} we introduced several mild selection cuts.
Implementing these cuts, and assuming that the final state leptons
could be either electrons or muons, {\bf (KK: factor of 4\ldots?)}
the SM cross section for $\ppprocess$ at
$14\,\mathrm{TeV}$ is $\sim 15.3\,\mathrm{fb}$; thus, the number of
events expected within the context of the HL-LHC is $\sim
15.3\,\mathrm{fb} \times 3000\,\mathrm{fb}^{-1} = 4.59\times
10^4$. This number is expected to be larger
if $\kpt\neq 0$ (assuming $\kp=1$),
since the corresponding cross section is
larger than the SM cross section in this case.
Taking into account NLO corrections (to the
production process) via a $K$ factor of approximately
$1.2$~\cite{Dawson,Beenakker,Dittmaier}, we find that
the expected number of
events increases to $\sim 5.49 \times 10^4$.
{\bf (KK: should we use 5.5 at this point, since
  the $K$ factor is only two sig figs?)}
On the other hand, additional cuts, as
well as a reduction in efficiency related to momentum reconstruction,
will lead to a decrease in this number.  In
order to measure the asymmetry $\mathcal{A}(\epsilon_4)$,
for example, the $t$ and $\tbar$
momenta need to be reconstructed. This is challenging, not only due to
the presence of two neutrinos in the final state (which escape the
detector undetected), but also because final state objects need to be
associated with their respective parent quark~\cite{atlasconf}.
{\bf (KK: maybe we can talk about this for a minute; I don't think I
  understand it\ldots.  Wait -- do we mean that the quarks and leptons
  need to be associated with either the top or antitop?  If so, maybe
  we can reword this a bit.  Suggestion follows\ldots, maybe this
  is too explicit now, because we also wanted it to refer to the Higgs.)}
but also because the (visible) quarks and charged leptons in the final
state need to be correctly associated with the corresponding
parent particle (i.e., the top or antitop quark)~\cite{atlasconf}.
As was
already noted in Sec.~\ref{sec5}, one possibility is to use the
neutrino weighting technique along with the kinematic equations
arising from kinematic constraints related to the top and $W$ masses
as well as from the energy-momentum conservation at each of the decay
vertices involved in the process. {\bf (KK: Can we either simplify the
  previous sentence or split it
  into 2 or 3 sentences?  I'm not 100\% clear on which ideas go
  together, so I wonder if one of you could give it a try.  My preference
  would be to simplify it to something like ``\ldots weighting technique,
  along with associated kinematic constraints'' or something like
  that, and then give a reference.)}
Within the context of $t\tbar$ production {\bf (KK: correct?)} this
procedure has been used, for instance, to obtain 
spin correlation~\cite{atlasconf} and charge
asymmetry~\cite{atlascharge} measurements.
Also, events reconstructed using this technique have
been used in the analysis of angular distributions that
are useful for discriminating the signal from the backgrounds in
$t\tbar H (H\rightarrow b\bbar)$~\cite{dosSantos}.
{\bf (KK: do we need an initial state
  on this process?)} In all these cases the corresponding
efficiency in the reconstruction of the momenta is up to $\sim 80\%$.
{\bf (KK: Does this mean that none of them exceeds 80\% or that
  they all have an efficiency of at least 80\%?)}

Given the discussion in the previous paragraph, we
have generated sets of $5\times 10^4, 1\times 10^4$ and $5\times 10^3$
events and have recalculated the most sensitive observable, 
$\mathcal{A}(\epsilon_4)$, for each case. The results are displayed in
Table \ref{table11}, where it can be seen that for $5\times 10^4$ events
(which is close to our rough estimate above for the
total number of signal events for the
HL-LHC), {\bf (KK: stated correctly?)}
the observable is still very sensitive to $\kpt$.
In this case, the $\mathrm{CP}$-mixed scenarios are
effectively separated by $19\sigma$. As expected, the
sensitivity worsens as the number of events is reduced, but even with
$5\times 10^3$ events the separation between the $\mathrm{CP}$-mixed
scenarios under consideration is $\sim 6.5\sigma$. \par

In Sec.~\ref{sec5} we defined the TP combination $\epsilon_{10}$,
which does not depend directly on the top or antitop momenta.
Although the top and antitop momenta would not need to be
reconstructed to measure $\mathcal{A}(\epsilon_{10})$,
it is still useful to examine this observable for more
conservative numbers of events. Table~\ref{table12} shows the
results obtained for 
$5\times 10^4$ and $1\times 10^4$ events. We see in this case
that even with $1\times 10^4$ events the observable is
able to distinguish the $\mathrm{CP}$-mixed cases by
$5.6\sigma$.\par

Finally, it is important to mention that a realistic
analysis of the sensistivity of the observables discussed in this
paper requires a study of the impact of the backgrounds, as well as
the hadronization of the quarks in the final state and the effects of
the detector. If we consider the dominant decay mode of the Higgs boson,
$H\rightarrow b\bbar$, in order to maximize the cross section of the
process, the signature is given by $4$ $b$-jets, two leptons and
missing energy.  The main background arises from the production of
$t\tbar$ in association with additional jets, with the dominant
source being the production of $t\tbar + b\bbar$.
In Ref.~\cite{chinos} it is shown that the application of a small
set of cuts results in a large improvement in the signal to background
ratio.  {\bf (KK: please check that I didn't say this incorrectly.)}
On the experimental side, a
rigorous treatment of the signal and backgrounds
for the process {\bf (KK: \ldots process\ldots)}
is performed in Ref.~\cite{atlasger}, using $20.3\,
\mathrm{fb}^{-1}$ of data at $\sqrt{s}=8\,\mathrm{TeV}$.
       {\bf (KK: please check that I didn't alter the meaning
         of this last sentence when I edited it.  Also, do we need
         to say anything about this study other than that it was done?)}

\begin{table}[th]
\caption{Asymmetry for the TP $\epsilon_4$ obtained using $5\times
  10^4, 1 \times 10^4$ and $5\times 10^3$ events for the SM
  case and the two $\mathrm{CP}$-mixed cases. }
\label{table11}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|========|}
%\hhline{|--------|}
\multirow{2}{*}{$\kappa_t$} & \multirow{2}{*}{$\tilde{\kappa}_t$} & \multicolumn{2}{c||}{$N_{\mathrm{ev}}=5\times 10^4$} & \multicolumn{2}{c||}{$N_{\mathrm{ev}}=1\times 10^4$} & \multicolumn{2}{c|}{$N_{\mathrm{ev}}=5\times 10^3$} \\ \cline{3-8}
& & $\mathcal{A}(\epsilon_4)$~~&$\mathcal{A}(\epsilon_4)/\sigma_{\mathcal{A}}$ &  $\mathcal{A}(\epsilon_4)$~~&$\mathcal{A}(\epsilon_4)/\sigma_{\mathcal{A}}$ &  $\mathcal{A}(\epsilon_4)$~~&$\mathcal{A}(\epsilon_4)/\sigma_{\mathcal{A}}$ \\
\hhline{|========|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $-0.0405$~~~ & $-9.1$~~~ & $-0.0426$~~~ & $-4.3$~~~ & $-0.0496$~~~ & $-3.5$~~~ \\[0.6mm]
\hline
$1$ & $0$ & $0.0004$~ & $0.1$~ & $-0.0084$~~~ & $-0.8$~~~ & $-0.0004$~~~ & $-0.03$~~~ \\[0.6mm]
\hline
$1$ & $1$ & $0.0443$~ & $9.9$~ & $0.0434$~ & $4.2$~ & $\,0.0420$~ & $3.0\,\,$ \\
\hhline{|========|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}

\begin{table}[th]
\caption{Asymmetry for the TP $\epsilon_{10}$ in the SM case and the
  two $\mathrm{CP}$-mixed cases for
  $5\times 10^4$ and $1\times 10^4$ events.}
\label{table12}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|======|}
%\hhline{|--------|}
\multirow{2}{*}{$\kappa_t$} & \multirow{2}{*}{$\tilde{\kappa}_t$} & \multicolumn{2}{c||}{$N_{\mathrm{ev}}=5\times 10^4$} & \multicolumn{2}{c|}{$N_{\mathrm{ev}}=1\times 10^4$} \\ \cline{3-6}
& & $\mathcal{A}(\epsilon_{10})$~~&$\mathcal{A}(\epsilon_{10})/\sigma_{\mathcal{A}}$ &  $\mathcal{A}(\epsilon_{10})$~~&$\mathcal{A}(\epsilon_{10})/\sigma_{\mathcal{A}}$ \\
\hhline{|======|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $-0.0270$~~~ & $-6.0$~~~ & $-0.0184$~~~ & $-1.8$~~~  \\[0.6mm]
\hline
$1$ & $0$ & $0.0022$~ & $0.5$~ & $-0.0086$~~~ & $-0.9$~~~  \\[0.6mm]
\hline
$1$ & $1$ & $0.0313$~ & $7.0$~ & $0.0380$~ & $3.8\,$ \\
\hhline{|======|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
%

The
results shown in Tables \ref{table11} and \ref{table12} reveal that
with $5\times 10^3$ and $1\times 10^4$ events, respectively, the
observables $\mathcal{A}(\epsilon_4)$ and $\mathcal{A}(\epsilon_{10})$
are still useful for testing $\kpt$. Without taking into account
the loss of events that would take place in a realistic 
experimental analysis, these numbers of events
correspond to a luminosity of $\sim
300\,$-$\,600\,\mathrm{fb}^{-1}$ for the SM and even smaller for the
$\mathrm{CP}$-mixed cases (due to their larger cross section). This range
of luminosities is in principle achievable in the short term by the
LHC. We note that in order to be fully conclusive about the required
luminosity, it is important to include the effects of hadronization,
detector resolution, reconstruction efficiencies and so
forth. Such an analysis, however, is beyond the scope of this
paper.
%%%%%%%%%%%% with Cuts
%51.46/17 -0.02 +- 0.08
%45.48/17  -1.09 +- 0.07
%65.60/17   0.96 +- 0.08
%28.84/17   0.02 +- 0.07
%%%%%%%
%9.13/17     0.01 +- 0.06
%9.05/17     -0.98 +- 0.07
%19.7/17     0.80 +- 0.07
%16.59/17    0.06 +- 0.07
%
%%%%%%%%%%%% without Cuts
%16.36/17    0.0022 +-0.06
%15.25/17    -0.82 +- 0.07
%12.80/17    0.81 +- 0.07
%19.38/17    0.11 +- 0.08
%%%%%%
%7.45/17    0.005 +- 0.06
%18.17/17   -0.77 +- 0.07
%9.59/17    0.73 +- 0.06
%12.39/17   0.09 +- 0.08
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec7}
%
In this paper we have presented a collection of $\mathrm{CP}$-odd
observables based on triple product correlations that are useful for
disentangling the relative sign between the scalar ($\kp$) and a
potential pseudoscalar ($\kpt$) top-Higgs couplings in the $t\tbar H$
production with both tops decaying leptonically. We have tested the
sensitivity of the proposed observables by considering three types of
observables: asymmetries, mean values and angular distributions.\par

Through the use of spinor techniques we have written the expression
for the differential cross section of the full process in such a
manner that the production and the decay parts are separated, although
connected by the spin vectors of the top and antitop which are given
in terms of the momenta of the leptons in the final state. Moreover,
we have indentified the terms linear in $\kp$ and $\kpt$ as those
involving TPs. Among these, we have explored the three that do not
involve the momenta of the incoming quarks/gluons and at the same time
incorporate both spin vectors: $\epsilon_1\equiv \TPa$,
$\epsilon_2\equiv \TPb$ and $\epsilon_3\equiv \TPc$.\par

We have found
that $\epsilon_{1,2,3}$ allow to distinguish between the
$\mathrm{CP}$-mixed hypotheses by more than $\sim 20\sigma$ in the
case of asymmetries and $\sim 10\sigma$ in the case of mean values
when $1 \times 10^5$ simulated events are used. Furthermore, we have
shown that the angular distributions asocciated with these TPs are
also sensitive to the value of $\kp$ and $\kpt$ exhibiting a phase
shift that varies according to the values taken by these couplings. On
the other hand, by exploring TPs that incorporate the momenta of the
Higgs and the leptons instead of the spin vectors we can conclude that
the observables studied here appear to be more sensitive when the spin
vectors are used.\par
